Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2022-03-11 reports/manuscript.Rmd
Remove params from manuscript file

documentclass     : "apa6"
classoption       : "man"
csl               : vancouver-brackets-meta.csl
output            : papaja::apa6_pdf
nocite            : "`r params$nocite_list`"
params:
  render_img: true
  nocite_list : true
  inc_tabs: true
---

@@

```{r desctable, eval=params$inc_tabs}
reviews_tables[[1]]$table
```

@@

```{r eduplot, eval=params$render_img, fig.width=plots[[1]]$dims[[1]], fig.height=plots[[1]]$dims[[2]], fig.cap="Education outcomes"}
plots[[1]]$plot
```

@@

```{r healthplot, eval=params$render_img, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes", dev='cairo_pdf'}
plots[[2]]$plot
```

>>>>

documentclass     : "apa6"
classoption       : "man"
csl               : vancouver-brackets-meta.csl
output:papaja::apa6_pdf
nocite            : "`r params$nocite_list`"
---

@@

```{r desctable, eval = TRUE, results="asis"}
reviews_tables[[1]]$table
```

@@

```{r eduplot, fig.width=plots[[1]]$dims[[1]], fig.height=plots[[1]]$dims[[2]], fig.cap="Education outcomes"}
plots[[1]]$plot
```

@@

```{r healthplot, fig.width=plots[[2]]$dims[[1]], fig.height=plots[[2]]$dims[[2]], fig.cap="Health and health-related behaviour outcomes", dev='cairo_pdf'}
plots[[2]]$plot
```
